Deeply Virtual Compton Scattering measurement off bound protons

### 2018-12-21 eg6-letters/incoherent/publication_version/incoherent_prl.tex
add version of the paper that fits the publication procedures

\begin{figure}[tb]
\includegraphics[width=7.5cm]{figs/handbag_incoherent.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
   incoherent DVCS process off $^4$He, where the four-vectors of the electrons, 
   photons, and protons are denoted by $k/k^\prime$, $q/q^\prime$, and 
   $p/p^\prime$, respectively. $x+\xi$ is the nucleon longitudinal momentum 
   fraction carried by the struck quark, -2$\xi$ is the longitudinal momentum 
   fraction of the momentum transfer $\Delta$ ($= q - q^\prime$), and 
   $t$~($=\Delta^2$) is the squared momentum transfer between the initial and
   the final state nucleon.}
\label{fig:diags}
\end{figure}

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value ($t_{min}$) at given $Q^2$ and $W$ defined as: 
\begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
ensured the exclusivity of the incoherent DVCS events by imposing a series of 
constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
\caption{The distributions from left to right and from top to bottom are: 
   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
   ($\theta$) between the measured and the calculated photons in the $e'p'$ 
   final-state system. The incoherent DVCS exclusivity cuts are represented by 
   the vertical red-dashed lines. The black distributions represent the 
   incoherent DVCS event candidates before the exclusivity cuts. The shaded 
   distributions represent the incoherent DVCS events that passed all of these 
   cuts except the quantity plotted.}
\label{fig:kin-cuts}

\end{figure}
\begin{figure}[h!]
\hspace{-0.45cm}
\includegraphics[width=9.0cm]{figs/Q2_xB_t_InCoh.pdf}
\caption{Incoherent DVCS event distributions for $Q^{2}$ as a function of 
$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the exclusivity 
cuts.}
\label{fig:kin-coverage}
\end{figure}

%background
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

@@

\begin{figure}[tb]
\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot the curves are theoretical 
   calculations from \cite{simonetta_2}. On the bottom plot the solid (empty) 
   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
   measurements for the incoherent (coherent) enriched region 
   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
   from \cite{simonetta_2}.  } \label{fig:alu90}
\end{figure}

@@

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
\includegraphics[width=7.8cm]{figs/ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray band 
   represents the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

\begin{figure}[tb]
\includegraphics[width=7.5cm]{handbag_incoherent.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
   incoherent DVCS process off $^4$He, where the four-vectors of the electrons, 
   photons, and protons are denoted by $k/k^\prime$, $q/q^\prime$, and 
   $p/p^\prime$, respectively. $x+\xi$ is the nucleon longitudinal momentum 
   fraction carried by the struck quark, -2$\xi$ is the longitudinal momentum 
   fraction of the momentum transfer $\Delta$ ($= q - q^\prime$), and 
   $t$~($=\Delta^2$) is the squared momentum transfer between the initial and
   the final state nucleon.}
\label{fig:diags}
\end{figure}

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value ($t_{min}$) at given $Q^2$ and $W$ defined as: 
\begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
ensured the exclusivity of the incoherent DVCS events by imposing a series of 
constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{incoh_exc_cuts_final.pdf}
\caption{The distributions from left to right and from top to bottom are: 
   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
   ($\theta$) between the measured and the calculated photons in the $e'p'$ 
   final-state system. The incoherent DVCS exclusivity cuts are represented by 
   the vertical red-dashed lines. The black distributions represent the 
   incoherent DVCS event candidates before the exclusivity cuts. The shaded 
   distributions represent the incoherent DVCS events that passed all of these 
   cuts except the quantity plotted.}
\label{fig:kin-cuts}
\end{figure}

%background
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

@@

\begin{figure}[tb]
\includegraphics[width=7.8cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.8cm]{ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=7.8cm]{ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot the curves are theoretical 
   calculations from \cite{simonetta_2}. On the bottom plot the solid (empty) 
   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
   measurements for the incoherent (coherent) enriched region 
   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
   from \cite{simonetta_2}.  } \label{fig:alu90}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=7.8cm]{ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray band 
   represents the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
